Reproducible Validation and Replication Studies in Nanoscale Physics

### 2020-09-21 tex/results.tex
Final tweak

\paragraph{Method:} The main difference between the original simulations and ours is that they solve a 2D problem with the 
full Maxwell equations, while we solve a 3D problem with the electrostatic approximation. 
We lack any information about their code implementations, discretization schemes, or solver.  
We computed extinction cross-section (scattering plus absorption) while Rockstuhl et al.\ present only scattering cross-section. 
Absorption dominates in intensity over scattering in the quasistatic regime, so these results are not directly comparable. 
Nevertheless, the quantity of interest is the wavelength at which the peaks occur, and the main peaks for scattering and absorption do occur at nearly the same frequency, in this regime. 
For example, Wiley et al.\ show simulation results for a silver nanocube where the main peaks in the spectra are aligned \cite{wiley-etal-2006}.

>>>>

\paragraph{Method:} The main difference between the original simulations and ours is that they solve a 2D problem with the 
full Maxwell equations, while we solve a 3D problem with the electrostatic approximation. 
We lack any information about their code implementations, discretization schemes, or solver.  
We computed extinction cross-section (scattering plus absorption) while Rockstuhl et al.\ present only scattering cross-section. 
Absorption dominates in intensity over scattering in the quasistatic regime, so these results are not directly comparable. 
When the resonance peaks are sharp and narrow, the wavelengths at which they occur in the scattering and absorption spectra are nearly the same.
For example, Wiley et al.\ show simulation results for a silver nanocube where the main peaks in the spectra are close \cite{wiley-etal-2006}.  
Since silicon carbide has more pronounced peaks than silver, the wavelength at which they occur in the extinction and scattering spectra are more closely aligned.
